Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-06-29 Documents/Euler/Benchmarks1D/draft.tex
Linear Waves

Several tests were used to assess the accuracy of the RKDG method implemented in thornado \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & -1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{Initial parameters for most of the tests described in this paper, from \citep{LiskaWendroff2003}~and \citep{Leveque2002}. The table shows initial density ($\rho$), velocity ($u$), and pressure ($p$) on both sides of a discontinuity located at $x_0$. These initial conditions are then advanced to time $T$.}
  \label{tab:testtable}
\end{center}
\end{table}
TAble 1 dispplays the initial data for the Riemann problems. ($\rho_L$, $u_L$ , $p_L$) denote the mass density, velocity, and pressure to the left of the interface at $x=x_0$;($\rho_R$, $u_R$,  $p_R$) refer to these same quantities to the right of the interface. The problem is advanced to time T.
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}. 
%\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

Test 12 is the Woodward-Collela blast wave problem, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9. At all positions, initial density is 1 and initial velocity is 0. Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right, and the test is advanced to 0.038 seconds. \citep{LiskaWendroff2003}. Test 13 shows Shock Entropy Wave interactions, advanced to 1.8 seconds.
%\clearpage
\subsection{Test 1: Sod's Shock Tube} 
The Sod's Shock tube test features examples of threee different types of waves. A shock wave appears around $x=0.85$. A contact discontinuity appears around $x=0.68$. A rarefaction wave appears between about $x=0.3$ and $x=0.5$.

>>>>

Several tests were used to assess the accuracy of the RKDG method implemented in thornado \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & -1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{Initial parameters for most of the tests described in this paper, from \citep{LiskaWendroff2003}~and \citep{Leveque2002}. The table shows initial density ($\rho$), velocity ($u$), and pressure ($p$) on both sides of a discontinuity located at $x_0$. These initial conditions are then advanced to time $T$.}
  \label{tab:testtable}
\end{center}
\end{table}
Table 1 dispplays the initial data for the Riemann problems. ($\rho_L$, $u_L$ , $p_L$) denote the mass density, velocity, and pressure to the left of the interface at $x=x_0$;($\rho_R$, $u_R$,  $p_R$) refer to these same quantities to the right of the interface. The problem is advanced to time T.
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, $x_{\mbox{\tiny L}}=0.1$ and $x_{\mbox{\tiny R}}=0.6$ in test 9 \citep{LiskaWendroff2003}, $x_{\mbox{\tiny L}}=-5$ and $x_{\mbox{\tiny R}}=15$ in test 10, and $x_{\mbox{\tiny L}}=-15$ and $x_{\mbox{\tiny R}}=5$ in test 11 \citep{Leveque2002}. 
%\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

Test 12 is the Woodward-Collela blast wave problem, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9. At all positions, initial density is 1 and initial velocity is 0. Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right, and the test is advanced to 0.038 seconds. \citep{LiskaWendroff2003}. Test 13 shows Shock Entropy Wave interactions, advanced to 1.8 seconds.
%\clearpage
\subsection{Linear Waves Tests}

\begin{figure}
  \begin{center}
	\includegraphics[width=.975\textwidth]{lw1den.png}
	\begin{tabular}{cc}
	  \includegraphics[width=.475\textwidth]{lw1vel.png} &
	  \includegraphics[width=.475\textwidth]{lw1prs.png}
	\end{tabular}
  \end{center}
  \caption{Results from linear waves tests, showing density (top), velocity (bottom left) and pressure (bottom right) computed at various times after a disturbance.}
  \label{fig:lw1}
\end{figure}
\clearpage

\begin{figure}
  \begin{center}
	\includegraphics[width=.975\textwidth]{lw2den.png}
	\begin{tabular}{cc}
	  \includegraphics[width=.475\textwidth]{lw2vel.png} &
	  \includegraphics[width=.475\textwidth]{lw2prs.png}
	\end{tabular}
  \end{center}
  \caption{Results from linear waves tests, showing density (top), velocity (bottom left) and pressure (bottom right) computed using different integration methods and compared with an initial condition.}
  \label{fig:lw2}
\end{figure}
\clearpage

\subsection{Test 1: Sod's Shock Tube} 
The Sod's Shock tube test features examples of three different types of waves. A shock wave appears around $x=0.85$. A contact discontinuity appears around $x=0.68$. A rarefaction wave appears between about $x=0.3$ and $x=0.5$.
